Finiteness in Cubical Type Theory

### 2020-07-06 sections/search.tex
finished explanation of n-ary product code

Next we turn to how we will represent functions.
In Agda there are three ways to pass function arguments: explicitly,
implicitly, and as an instance.
We will represent these three different versions with a data type:
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{arg-form}
\end{agdalisting}

>>>>

Next we turn to how we will represent functions.
In Agda there are three ways to pass function arguments: explicitly,
implicitly, and as an instance.
We will represent these three different versions with a data type:
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{arg-form}
\end{agdalisting}
And then we can make a type for functions in the general sense: a type which has
this sum type as a parameter.
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{generic-function}
\end{agdalisting}
And we can show that this is isomorphic to a normal function:
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/Nary.tex]{generic-function-iso}
\end{agdalisting}

This of course is only a representation of \emph{non}-dependent functions.
Dependent functions are defined in a similar way:
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{pi-iso}
\end{agdalisting}

Using both of these things, we can now define a generic type for multi-argument
functions:
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{multi-generic}
\end{agdalisting}
We can also define multi-argument dependent functions in a similar way.
Similarly to how we had to define two tuple types in order to avoid the
\(\top\)-terminated tuples, we have two definitions for multi-argument dependent
functions.
We only include the nonempty version here for brevity.
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{pi-arrs-plus}
\end{agdalisting}

Finally, this all allows us to define an isomorphism between generic
multi-argument dependent functions and their uncurried forms.
\begin{agdalisting}
  \ExecuteMetaData[agda/Data/Product/NAry.tex]{full-iso}
\end{agdalisting}
